Should geophysicists use gravity anomaly or gravity disturbance?

### 2018-05-15 manuscript/letter.tex
Remove extra "is"
Reword the key question of the article
Include a phrase about how our approach will differ from the ones in the
literature.

The \textit{gravity vector} is the sum of the gravitational and centrifugal
accelerations felt by a body at rest on the Earth's surface.
Its intensity is what is geoscientists call \textit{gravity}
\citep{heiskanen-moritz1967, hofmann-wellenhof-moritz2005}.
When measured on moving platforms (e.g., airplanes,
helicopters, marine vessels), there are additional
non-gravitational accelerations due to the motion of the vehicle,
such as the Coriolis acceleration and high-frequency vibrations
\citep{glennie-etal2000,nabighian-etal2005-grav,baumann-etal2012}.
Geodesists use gravity measurements to estimate the Geoid \citep{li2001}
whereas geophysicists use gravity to estimate the Earth's
internal density distribution.
Hence, geophysicists are usually only interested
in the gravitational component of the observed gravity
because that is what that reflects the Earth's internal density distribution.

@@

We present a discussion with the aim of shedding some light on the question:
\textit{should we use the gravity disturbance or gravity anomaly in geophysical
applications}?
The concepts discussed here are well-established in the literature.
However, the debate around this theoretical issue has been
carried about from a more geodetic than a geophysical point of view
\citep{lafehr1991,chapin1996,li2001,fairhead2003,
hackney-featherstone2003,hinze2005}.
Our reasoning suggests that the gravity disturbance is more appropriated for
geophysical purposes than the gravity anomaly.

>>>>

The \textit{gravity vector} is the sum of the gravitational and centrifugal
accelerations felt by a body at rest on the Earth's surface.
Its intensity is what geoscientists call \textit{gravity}
\citep{heiskanen-moritz1967, hofmann-wellenhof-moritz2005}.
When measured on moving platforms (e.g., airplanes,
helicopters, marine vessels), there are additional
non-gravitational accelerations due to the motion of the vehicle,
such as the Coriolis acceleration and high-frequency vibrations
\citep{glennie-etal2000,nabighian-etal2005-grav,baumann-etal2012}.
Geodesists use gravity measurements to estimate the Geoid \citep{li2001}
whereas geophysicists use gravity to estimate the Earth's
internal density distribution.
Hence, geophysicists are usually only interested
in the gravitational component of the observed gravity
because that is what that reflects the Earth's internal density distribution.

@@

We present a discussion of whether the gravity disturbance or the gravity
anomaly should be used in geophysical applications.
The concepts discussed here are well-established in the literature.
However, the debate around this theoretical issue has been
carried about from a more geodetic than a geophysical point of view
\citep{lafehr1991,chapin1996,li2001,fairhead2003,
hackney-featherstone2003,hinze2005}.
We will approach the topic by comparing the geophysical interpretations of the
disturbance and the anomaly.
Our reasoning suggests that the gravity disturbance is more appropriated for
geophysical purposes than the gravity anomaly.
